Linear response theory for core set identification

### 2012-06-01 writedown/linear.response/langevin.tex
add results to langevin.tex

The phase space imcompressibility condition is assumed:

@@

where $\fwg$ is the forward infiniesimal generator gieven by

@@

stochasitc process denoted by $\vect Y_\alpha$:

@@

  \Big\} \\

@@

with initial condistions:

@@

>>>>

The phase space incompressibility condition is assumed:

@@

where $\fwg$ is the forward infiniesimal generator given by

@@

stochastic process denoted by $\vect Y_\alpha$:

@@

  \Big\} \\ \label{eqn:main}

@@

with initial conditions:

@@

\begin{figure}
  \centering
  \includegraphics[width=0.35\textwidth]{figs/fig-pot.eps}
  \caption{The potential with and without perturbation.}
  \label{fig:tmp1}
\end{figure}

\section{Numerical test}

We test the idea by a one-dimensional model system: one particle in a
double-well potential. For convenience, we let the mass of the
particle to be 1 \textsf{amu}. The Hamiltonian of the system is given
by:
\begin{align}
  \mh (\vect p, \vect q) = \frac 12 \vect p^2 + U(\vect q) 
\end{align}
with
\begin{align}
  U(\vect q) = \frac12 k (\vect q^2 - a^2)^2
\end{align}
Here $k = 8$ $\textsf{kJ} / (\textsf{mol nm}^4)$, and $ a = 1 \textsf{nm}$.
Notice at room temperature $300 \textsf{K}$, $k_BT = 2.48$ \textsf{kJ/mol}.
See the red line in Fig.~\ref{fig:tmp1}.
%$\textsf{kJ} / (\textsf{mol nm}^4)}$
The perturbation is given by
\begin{align}
  \vect C(\vect p, \vect q) = 0; \qquad
  \vect D(\vect p, \vect q) = -\nabla_{\vect q} V(\vect q) = 1
\end{align}
Here $V(\vect q) = -\vect q$, which effectively tilt the original
potential $U(\vect q)$. The strength of the perturbation $F_e(t)$ is given
by the following function:
\begin{align}
  F_e(t) = 
  \begin{cases}
    F_e^{\textrm{max}}\times (t / t_c) & t < t_c \\
    F_e^{\textrm{max}} & t \geq t_c
  \end{cases}
\end{align}
$t_c = 100$ \textsf{ps} so that the perturbation increases slow
enough: the typical decaying time scale of the correlation function
in~\eqref{eqn:main} is roughly 3 \textsf{ps}.  We choose $\mt_\alpha$
to be the propagator of the Langevin dynamics at temperature $150$
\textsf{K} with $\alpha = 1$ \textsf{ps}.  Since the dynamics is in
1-d, the projection is identity.  We consider the stability of the
distribution $f_t$ at time $t$: $-\Delta\mt_\alpha f_t$. The smaller
this value, the more stable the core sets are.

See Fig. \ref{fig:tmp2} and \ref{fig:tmp3} for numerical result.  Both
the direct non-equilirbium simulaiton and the linear response
approximation are presented. Time slice $t = 1$, 30, 60 and 100
\textsf{ps} are shown.  When the perturbation is small,
i.e. $F_e^{\textrm{max}} = 2$, the direct non-equilibrium simulation
and the linear response results consistent very well. As the
perturbation grows stronger, the left well becomes less stable, while
the right well becomes more stable.  When the perturbation is big,
i.e. $F_e^{\textrm{max}} = 6$, the linear response results are no
longer precise. When $t\geq 60$ \textsf{ps}, the left well basically
disappears, however, the linear response calculation present a well
that is nearly as stable as the right well.

\begin{figure}
  \centering
  \includegraphics[width=0.95\textwidth]
  {figs/warm100.str2.0.nst1e09.smallgrid/fig-2d.eps}
  \caption{The stability of distribution $f_t$ under perturbation of
    $F_e^{\textrm{max}} = 2$.
    Upper row: the direct non-equilibrium simulation. Lower row: the
    results of linear response formula~\eqref{eqn:main}.
  }
  \label{fig:tmp2}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.95\textwidth]
  {figs/warm100.str6.0.nst1e09.smallgrid/fig-2d.eps}
  \caption{The stability of distribution $f_t$ under perturbation of
    $F_e^{\textrm{max}} = 6$.  Upper row: the direct non-equilibrium
    simulation. Lower row: the results of linear response
    formula~\eqref{eqn:main}.  }
  \label{fig:tmp3}
\end{figure}
